---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# Functional Model-Based Discrimination and Clustering using wavelets

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/Erwangf/funHDDC-wavelet.svg?branch=master)](https://travis-ci.org/Erwangf/funHDDC-wavelet)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->


The R package `funHDDCwavelet` allows to perform time series clustering, via 
discrete wavelet transform, and modeling wavelet coefficients with a 
parcimonious gaussian mixture model. Parameter estimation is done with an EM 
algorithm.

## Installation

You can install the released version of funHDDCwavelet from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("funHDDCwavelet")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Erwangf/funHDDC-wavelet")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(funHDDCwavelet)
## basic example code
```



# Acknowledgements
This research benefited from the support of the FMJH ’Program Gaspard Monge for optimization and operations research and their interactions with data science’, and from the support from EDF and Thales.


